One-dimensional Classical Gas in a Harmonic Trap with Repulsive Interaction

### 2017-10-24 draft_02_zhiyu02.tex
Oct_19_2017

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.6]{ZhiyuPictures/N=5_GS_pre_2_rev.eps}
\caption{particles' position at ground states }
\label{fig:GS1}
\end{figure}

%\begin{figure}[hbtp]
%\centering
%\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/Eg1.eps}
%\caption{ground state Energy with $F_0$}
%\end{figure}
%\end{comment}

@@

Since the number of particles we use in the Molecular Dynamics simulation is limited (5 to 50), the
random noise is significant. If we start with a state whose configuration in phase-space is an
ellipse slightly deviated from circle, the oscillating amplitude will be too small to be
distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x,
zero p) and observe the oscillation of R(t).
\begin{figure}[hbtp]
\center
\includegraphics[scale=0.32]{ZhiyuPictures/freq_scanF_differentE_log_2_with_oscillation_demo.png}
\caption{breathing mode frequency measured at different E and $F_0$. Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation behavior of radius R(t) defined in Eq.\ref{eq:def_of_R}. The breathing frequency is measured by taking Fourier transformation of R(t).}
\label{fig:Breathingfrequency1}
\end{figure}

@@

\begin{figure*}
%\subfigure[$t=0$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=1-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=1-5T_rev.eps}
%\end{minipage}
%}
%\subfigure[$t=\frac{1}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/%stationary_frame_t=2-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=2-5T_rev.eps}
%\end{minipage}
%}\subfigure[$t=\frac{2}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=3-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=3-5T_rev.eps}
%\end{minipage}
%}\subfigure[$t=\frac{3}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=4-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=4-5T_rev.eps}
%\end{minipage}
%}\subfigure[$t=\frac{4}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=5-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=5-5T_rev.eps}
%\end{minipage}
%}
\includegraphics[width=0.9\textwidth]{ZhiyuPictures/stationary_and_rotating_frame_t=1-5_5T.eps}

@@

\begin{figure}
\centering
\includegraphics[scale=0.3]{ZhiyuPictures/bounce.png}
\includegraphics[scale=0.32]{ZhiyuPictures/pass.png}
\caption{a schematic diagram of the collision process: \textbf{(a)}(Upper)when $F_0*\sigma$ is big, particles can not penetrate each other, thus their trajectory in rotating frame is a circular arc.  \textbf{(b)} (Lower) When $F_0*\sigma$ is small, particles easily pass each other, so that the force they feel is not continuous, their trajectory has a turning point(the dashed bright blue trajectory is identical with the one in the upper figure, which is the critical situation between passing and bouncing, that is to say, particles have zero relative velocity when they collide.) }
\label{fig:Breathingfrequency3}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre_Font18.eps}
\caption{dependence of breathing frequency on Energy, N=20. Different color stands for different $F_0$: Red for $F_0$=2000; Yellow for $F_0$=3000; Green for $F_0$=10000;  Blue for $F_0$=100000. Run with 3 different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles). The black dashed line is the prediction of Eq.\ref{eq:breathingfrequency1}.}
\label{fig:Breathingfrequency4}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
\includegraphics[scale=0.2]{ZhiyuPictures/effective_potential.png}
\caption{effective potential for two-particle system}
\label{fig:thermalization2}
\end{figure}

@@

\begin{figure}

\subfigure[$E_i=2$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=2_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=2_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=3$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=3_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=3_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=5$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=5_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=5_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=10$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[scale=0.3]{ZhiyuPictures/10_23_N=2_F0=1_Er=10_single_particle_energy_pre.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=10_phasespace.eps}
\end{minipage}
}

\caption{the dependence of beat frequency on internal energy. The diagram is the energy of two particles. Here, $F_0$ is set to be 1. In this case, the larger $E_i$ is, the lower the beat frequency is. \label{fig:thermalization1}}%Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{ZhiyuPictures/pair1_pre.eps}
\caption{evolution of single-particle energy}
\label{fig:thermalization4}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
%\includegraphics[scale=0.2]{ZhiyuPictures/distribution1_scanF0_E=100_3.eps}
%\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
\includegraphics[scale=0.5]{ZhiyuPictures/N=5_energydistribution_pre_rev1.eps} 
\includegraphics[scale=0.5]{ZhiyuPictures/N=10_energydistribution_pre_rev1.eps}
\includegraphics[scale=0.5]{ZhiyuPictures/N=20_energydistribution_pre_rev1.eps}
\caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, {\color{green}{green}} curves corresponds to Boltzmann distribution; {\color{red}{red}} curves are obviously non-Boltzmann, while the {\color{yellow}{yellow}} ones are intermediate case, represent ``thermalization threshold". In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500$-$F_0=1000$, which is consistent with our prediction in Eq.\ref{eq:thermalizatiton condition}}
\label{fig:thermalization5}

@@

\begin{figure}
\includegraphics[width=0.5\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_Font12_s.eps} 
\caption{energy of each particle, $F_0=200$}
\label{fig:thermalization6}

\includegraphics[width=0.5\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_Font12_s.eps} 
\caption{energy of each particle, $F_0=1000$}
\label{fig:thermalization7}
\end{figure}

As is shown in Fig.\ref{fig:thermalization5} above, the critical point for reaching ``Boltzmann-like" distribution (later we will verify that it is Boltzmann distribution) is $F_0=500$-$F_0=1000$ (we always set $\sigma=1$), while the average energy $\sim 1000$, as we expected, they are of the same order. As a supplementary proof of our argument, Fig.\ref{fig:thermalization6} and Fig.\ref{fig:thermalization7} show the great difference of single-particle energy between two examples of below and above the thermalization threshold ($F_0=200$ $\&$ $F_0=1000$ for $N=10, E=10000$): in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic. To date, we have verified that the threshold of thermalization, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution in two side of the threshold.

@@

\begin{figure}[hbtp]
\centering
%\includegraphics[scale=0.5]{ZhiyuPictures/distribution_at_N=5_F0=10000_pre.eps}
%\caption{Energy distribution, N=5, F0=10000}
%\label{fig:thermalization8}

\includegraphics[scale=0.5]{ZhiyuPictures/boltzmann_N=10_F=10000_pre_rev.eps}
\caption{Energy distribution, N=10, F0=10000}
\label{fig:thermalization9}

\includegraphics[scale=0.5]{ZhiyuPictures/boltzmann_N=20_F=10000_pre_rev.eps} 
\caption{Energy distribution, N=20, F0=10000}
\label{fig:thermalization10}
\end{figure}

@@

\begin{figure}[hbtp]
\centering
%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot1_screenshot.png}
\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot2_screenshot.png}
\caption{LLE distribution for N=5, F0=1000, scan E. The size of bin is 0.01}\label{fig:LLEdistribution1}
\end{figure}

%\begin{figure}[hbtp]
%\centering
%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone1_screenshot.png}
%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone2_screenshot.png}
%\caption{``bone". top(bottom):modified(reversed)}
%\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[scale=0.5]{ZhiyuPictures/N=50_F=1000_E=30000_shapemovie_interval0_628_2_500s.eps}
\caption{Distribution in phase-space after evolving for about 500 time units ($N=50, F_0=1000, E=30000$). Please notice that the yellow(red) arrows shows the length of long(short) axis of inertia ellipse, which is prependicular to the long(short) axis of distribution cloud. For instance, if the yellow arrow lies in p-axis, it means the long axis of distribution cloud is lying along x-axis.}\label{fig:N=50_F=1000_E=30000_movie}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.4]{ZhiyuPictures/quadrupole_mode_2.png}
\caption{Schemetic description of the excited mode.  Red ellipse is the shape of cloud in low-energy regime when there is repulsive interaction. Gray cloud is the imaginary shape of cloud when there is no interaction, they are plotted here as a reference. One may think of the effect of interaction as a kind of potential that prefer to place particles along x axis, because in low energy regime the system is not allowed to be squeezed too much along x axis since doing this cost a large amount of interaction energy.}\label{fig:Schemetic_description_of_the_mode}
\end{figure*}

@@

\begin{comment}
\section{others(those I haven't organized it into the text in logical order but may be useful)}

\subsection{Evolution of $R(t)$ and $\sqrt{\delta^2R(t)}/R(t)$} 
Results are shown in Fig.\ref{fig:others1}

\begin{figure}[hbtp]

\centering
\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/fluc_of_R_with_time2.eps}
\caption{fluctuation of R with time }
sigma=0.01(short range), $F_0=0.1(black), 1(blue), 10(green) ,100(red)$
\label{fig:others1}
\end{figure}

\subsection{Detailed discussion of two-particle motion}
{\color{red}{This chapter previously follow the subsection ``two-particle case" in subsection ``Dynamics study" in section ``Thermalization". But then I found we haven't used these result. So I put it at the end for the time being}}.

From now on, let's stand in the the frame of center of mass to observe the motion of two-particle system. In this frame, without interaction, we will find two particles sitting symmetrically in an equivalent harmonic trap (black curve), whose shape is identical to the trap we see in the static frame. As a result, there frequency of relative motion is exactly $2\omega$(since two particle are identical). We label the position of center of mass as 0. And we may only analyze the motion on positive axis since positive and negative are symmetric.

Now, let's consider the interaction between them. Because of interaction, the potential curve between $+-\frac{\sigma}{2}$ should be modified to another parabolic curve that simultaneously satisfies the following two condition:\\
1) intersect with black curve at $+-\frac{\sigma}{2}$\\
2) minima is $+-\frac{F_0}{m\omega_0^2}$, which comes from a simple harmonic oscillator with an extra constant force $F_0$\\
Thus, it is obvious that by comparing $\frac{F_0}{m\omega_0^2}$ and $\sigma$, we can at least divide our parameter into several regime:\\
1) When $\frac{F_0}{m\omega_0^2\sigma}>0.5$, we will have the blue curve (see figure \ref{fig:thermalization2})\\
2) When $\frac{F_0}{m\omega_0^2\sigma}<0.5$, the red curve\\
3) When $\frac{F_0}{m\omega_0^2\sigma}=0.5$, the green one.\\
For those three types of curve, the significant difference is only at low energy case:\\
For the red one, particle will oscillate at constant frequency $\omega$;
For the blue one, when energy is lower, since the first derivative of the curve in the neighbourhood is non-zero, the frequency goes to infinity;
For the green curve, in low energy limit, it takes finite time to finish half period of oscillation, while infinitesimal time is spent on the slope part. Thus, frequency will converge to  $2\omega$.

\begin{figure}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_1.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_2.png} 
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.3\textwidth}
\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_3.png} 
\end{minipage}
}
\centering
\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value of $\frac{F_0}{m\omega_0^2\sigma}$
\label{fig:thermalization3}
\end{figure}
\end{comment}

>>>>

\begin{figure}[h]
\centering
\includegraphics[scale=0.6]{ZhiyuPictures/N=5_GS_pre_2_rev.eps}
\caption{particles' position at ground states }
\label{fig:GS1}
\end{figure}

%\begin{figure}[h]
%\centering
%\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/Eg1.eps}
%\caption{ground state Energy with $F_0$}
%\end{figure}
%\end{comment}

@@

Since the number of particles we use in the Molecular Dynamics simulation is limited (5 to 50), the
random noise is significant. If we start with a state whose configuration in phase-space is an
ellipse slightly deviated from circle, the oscillating amplitude will be too small to be
distinguished from noise. Therefore, we start from an extreme case -- line distribution (random x,
zero p) and observe the oscillation of R(t).
\begin{figure}[h]
\center
\includegraphics[scale=0.32]{ZhiyuPictures/freq_scanF_differentE_log_2_with_oscillation_demo.png}
\caption{breathing mode frequency measured at different E and $F_0$. Insert: a demonstration of oscillation, $E_{trap}$ is the total potential energy of particles in the trap, which is proportional to $\sum_{is}{x_i^2}$, thus manifest the oscillation behavior of radius R(t) defined in Eq.\ref{eq:def_of_R}. The breathing frequency is measured by taking Fourier transformation of R(t).}
\label{fig:Breathingfrequency1}
\end{figure}

@@

\begin{figure*}[h]
%\subfigure[$t=0$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=1-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=1-5T_rev.eps}
%\end{minipage}
%}
%\subfigure[$t=\frac{1}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/%stationary_frame_t=2-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=2-5T_rev.eps}
%\end{minipage}
%}\subfigure[$t=\frac{2}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=3-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=3-5T_rev.eps}
%\end{minipage}
%}\subfigure[$t=\frac{3}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=4-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=4-5T_rev.eps}
%\end{minipage}
%}\subfigure[$t=\frac{4}{5}T$]{
%\begin{minipage}[b]{0.18\linewidth}
%\includegraphics[scale=0.21]{ZhiyuPictures/stationary_frame_t=5-5T_rev.eps} 
%\includegraphics[scale=0.22]{ZhiyuPictures/rotating_frame_t=5-5T_rev.eps}
%\end{minipage}
%}
\includegraphics[width=0.9\textwidth]{ZhiyuPictures/stationary_and_rotating_frame_t=1-5_5T.eps}

@@

\begin{figure}[h
]
\subfigure[]{
\begin{minipage}[b]{0.4\textwidth}
\includegraphics[width=1\textwidth]{ZhiyuPictures/bounce.png}
\end{minipage}
}
\subfigure[]{
\begin{minipage}[b]{0.4\textwidth}
\includegraphics[width=1\textwidth]{ZhiyuPictures/pass.png}
\end{minipage}
}

\caption{a schematic diagram of the collision process: \textbf{(a)}When $F_0\sigma$ is large, particles can not pass each other. Subduing to a constant repulsive force in collision, their trajectory in rotating frame is a circular arc.  \textbf{(b)} When $F_0\sigma$ is small, particles easily pass each other, so that the force they feel is not continuous. Their trajectory has a turning point. The dashed bright blue trajectory is identical with the one in (a), which is the critical situation between passing and bouncing. In that case, particles have zero relative velocity when they collide. }
\label{fig:Breathingfrequency3}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.6]{ZhiyuPictures/freq_scanF_scanE_pre_Font18.eps}
\caption{dependence of breathing frequency on Energy, N=20. Different color stands for different $F_0$: Red for $F_0=2\times10^3$; Yellow for $F_0=3\times10^3$; Green for $F_0=1\times10^4$;  Blue for $F_0=1\times10^5$. Run with three different initial states in each case, and in each run, measure the frequency in 0-100 time unit(label as crosses) and in 900-1000 time unit (label as circles). The black dashed line is the prediction of Eq.\ref{eq:breathingfrequency1}.}
\label{fig:Breathingfrequency4}
\end{figure}

@@

\begin{figure}[h]
\centering
\includegraphics[scale=0.2]{ZhiyuPictures/effective_potential.png}
\caption{effective potential for two-particle system}
\label{fig:thermalization2}
\end{figure}

@@

\begin{figure}[h]

\subfigure[$E_i=2$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=2_single_particle_energy_600_500_Font24.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=2_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=3$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=3_single_particle_energy_600_500_Font24.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=3_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=5$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=5_single_particle_energy_600_500_Font24.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=5_phasespace.eps}
\end{minipage}
}
\subfigure[$E_i=10$]{
\begin{minipage}[b]{0.22\textwidth}
\includegraphics[width=1\textwidth]{ZhiyuPictures/10_23_N=2_F0=1_Er=10_single_particle_energy_600_500_Font24.eps} 
%\includegraphics[scale=0.2]{ZhiyuPictures/twoparticle_Er=10_phasespace.eps}
\end{minipage}
}

\caption{the dependence of beat frequency on internal energy. The diagram is the energy of two particles. Here, $F_0$ is set to be 1. In this case, the larger the $E_i$, the lower the beat frequency. \label{fig:thermalization1}}%Actually in very low energy, we can retrieve a beat, but that is for different reason -- it is a beat between $\omega_0$ and $\frac{\omega_0}{2}+\delta $

@@

\begin{figure}
\centering
\includegraphics[scale=0.5]{ZhiyuPictures/pair1_pre.eps}
\caption{Time evolution of single-particle energy}
\label{fig:thermalization4}
\end{figure}

@@

\begin{figure}[h]
\centering
%\includegraphics[scale=0.2]{ZhiyuPictures/distribution1_scanF0_E=100_3.eps}
%\caption{Distribution scan $F_0$, $E=100$, $N=5$, $\sigma=1$ {\color{red}{Run again!}} }
\includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=5_energydistribution_500_400_Font16.eps} 
\includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=10_energydistribution_500_400_Font16.eps}
\includegraphics[width=0.32\textwidth]{ZhiyuPictures/N=20_energydistribution_500_400_Font16.eps}
\caption{the energy distribution measured in $\sim 10000$ time units, as will be verified later, Green curves corresponds to Boltzmann distribution; Red curves are obviously non-Boltzmann, while the yellow ones are intermediate case, represent ``thermalization threshold". In three figures for different N, we choose E/N identical (=1000), and thermalization is reached at $F_0=500\sim1000$, which is consistent with our prediction in Eq.\ref{eq:thermalizatiton condition}}
\label{fig:thermalization5}

@@

%\begin{figure}
%\subfigure[N=10, $F_0=200$]{
%\begin{minipage}[b]{0.4\linewidth}
%\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_Font12_s.eps} 
%\label{fig:thermalization6}
%\end{minipage}
%}

%\subfigure[N=10, $F_0=1000$]{
%\begin{minipage}[b]{0.4\linewidth}
%\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_Font12_s.eps} 
%\label{fig:thermalization7}
%\end{minipage}
%}

%\end{figure}

\begin{figure}[h]
\subfigure[N=10, $F_0=200$]{
\begin{minipage}[b]{0.4\linewidth}
\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=200_s_400_300_Font12.eps}
\label{fig:thermalization6}
\end{minipage}
}
\subfigure[N=10, $F_0=1000$]{
\begin{minipage}[b]{0.4\linewidth}
\includegraphics[width=1\textwidth]{ZhiyuPictures/N=10_single_particle_energy_F0=1000_s_400_300_Font12.eps} 
\label{fig:thermalization7}
\end{minipage}
}

\caption{Time evolution of the particles' energy $\epsilon$}

As is shown in Fig.\ref{fig:thermalization5} above, the critical point for reaching ``Boltzmann-like" distribution (later we will verify that it is Boltzmann distribution) is $F_0=500\sim1000$ (we always set $\sigma=1$), while the average energy $\sim 1000$, as we expected, they are of the same order. As a supplementary proof of our argument, Fig.\ref{fig:thermalization6} and Fig.\ref{fig:thermalization7} show the great difference of single-particle energy between two examples of below and above the thermalization threshold ($F_0=200$ $\&$ $F_0=1000$ for $N=10, E=10000$): in the former one there is always some particle maintained at high excitation, while in the latter the system probably goes to ergodic. To date, we have verified that the threshold of thermalization, which is $\frac{NF_0\sigma}{E}\sim1 $ , and corresponding feature of their energy distribution in two side of the threshold.

@@

%\begin{figure*}
%%\includegraphics[scale=0.5]{ZhiyuPictures/distribution_at_N=5_F0=10000_pre.eps}
%%\caption{Energy distribution, N=5, F0=10000}
%%\label{fig:thermalization8}
%\subfigure[N=10, $F_0=1\times10^4$]{
%\begin{minipage}[b]{0.1\textwidth}
%\includegraphics[scale=0.1]{ZhiyuPictures/boltzmann_N=10_F=10000_pre_rev.eps}
%\caption{Energy distribution, N=10, $F_0=1\times10^4$}
%\label{fig:thermalization9}
%\end{minipage}
%}

%\subfigure[N=20, $F_0=1\times10^4$]{
%\begin{minipage}[b]{0.1\textwidth}
%\includegraphics[scale=0.1]{ZhiyuPictures/boltzmann_N=20_F=10000_pre_rev.eps} 
%\caption{Energy distribution, N=20, $F_0=1\times10^4$}
%\label{fig:thermalization10}
%\end{minipage}
%}

%\end{figure*}

\begin{figure}[h]
\subfigure[N=10, $F_0=1\times10^4$]{
\begin{minipage}[b]{0.4\linewidth}
\includegraphics[width=1\textwidth]{ZhiyuPictures/boltzmann_N=10_F=10000_500_400_Font16.eps}
\label{fig:thermalization9}
%\caption{Energy distribution, N=10, $F_0=1\times10^4$}
\end{minipage}
}
\subfigure[N=20, $F_0=1\times10^4$]{
\begin{minipage}[b]{0.4\linewidth}
\includegraphics[width=1\textwidth]{ZhiyuPictures/boltzmann_N=20_F=10000_500_400_Font16.eps} 
\label{fig:thermalization10}
%\caption{Energy distribution, N=20, $F_0=1\times10^4$}
\end{minipage}
}

\caption{Fitting energy distribution $\rho(\epsilon)$ with Boltzmann distribution}

@@

\begin{figure}[h]
\centering
%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot1_screenshot.png}
\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_hot2_screenshot.png}
\caption{LLE distribution for N=5, F0=1000, scan E. The size of bin is 0.01}\label{fig:LLEdistribution1}
\end{figure}

%\begin{figure}[h]
%\centering
%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone1_screenshot.png}
%\includegraphics[scale=0.4]{ZhiyuPictures/LLEdistribution_1_11_pre_bone2_screenshot.png}
%\caption{``bone". top(bottom):modified(reversed)}
%\end{figure}

@@

\begin{figure*}
\centering
\includegraphics[scale=0.5]{ZhiyuPictures/N=50_F=1000_E=30000_shapemovie_interval0_628_2_500s_1100_600_Font18.eps}
\caption{Distribution in phase-space after evolving for about 500 time units ($N=50, F_0=1000, E=30000$). Please notice that the yellow(red) arrows shows the length of long(short) axis of inertia ellipse, which is prependicular to the long(short) axis of distribution cloud. For instance, if the yellow arrow lies in p-axis, it means the long axis of distribution cloud is lying along x-axis.}\label{fig:N=50_F=1000_E=30000_movie}
\end{figure*}

\begin{figure*}
\centering
\includegraphics[scale=0.4]{ZhiyuPictures/quadrupole_mode_2.png}
\caption{Schemetic description of the excited mode.  Red ellipse is the shape of cloud in low-energy regime when there is repulsive interaction. Gray cloud is the imaginary shape of cloud when there is no interaction, which is plotted here as a reference. One may think of the effect of interaction as a kind of potential that prefer to place particles along x axis, because in low energy regime the system is not allowed to be squeezed too much along x axis since doing this cost a large amount of interaction energy.}\label{fig:Schemetic_description_of_the_mode}
\end{figure*}

@@

%\begin{comment}
%\section{others(those I haven't organized it into the text in logical order but may be useful)}

%\subsection{Evolution of $R(t)$ and $\sqrt{\delta^2R(t)}/R(t)$} 
%Results are shown in Fig.\ref{fig:others1}

%\begin{figure}[h]

%\centering
%\includegraphics[scale=0.3]{D:/matlab2016/MolecularDynamics/figure/fluc_of_R_with_time2.eps}
%\caption{fluctuation of R with time }
%sigma=0.01(short range), $F_0=0.1(black), 1(blue), 10(green) ,100(red)$
%\label{fig:others1}
%\end{figure}

%\subsection{Detailed discussion of two-particle motion}
%{\color{red}{This chapter previously follow the subsection ``two-particle case" in subsection ``Dynamics study" in section ``Thermalization". But then I found we haven't used these result. So I put it at the end for the time being}}.

%From now on, let's stand in the the frame of center of mass to observe the motion of two-particle system. In this frame, without interaction, we will find two particles sitting symmetrically in an equivalent harmonic trap (black curve), whose shape is identical to the trap we see in the static frame. As a result, there frequency of relative motion is exactly $2\omega$(since two particle are identical). We label the position of center of mass as 0. And we may only analyze the motion on positive axis since positive and negative are symmetric.

%Now, let's consider the interaction between them. Because of interaction, the potential curve between $+-\frac{\sigma}{2}$ should be modified to another parabolic curve that simultaneously satisfies the following two condition:\\
%1) intersect with black curve at $+-\frac{\sigma}{2}$\\
%2) minima is $+-\frac{F_0}{m\omega_0^2}$, which comes from a simple harmonic oscillator with an extra constant force $F_0$\\
%Thus, it is obvious that by comparing $\frac{F_0}{m\omega_0^2}$ and $\sigma$, we can at least divide our parameter into several regime:\\
%1) When $\frac{F_0}{m\omega_0^2\sigma}>0.5$, we will have the blue curve (see figure \ref{fig:thermalization2})\\
%2) When $\frac{F_0}{m\omega_0^2\sigma}<0.5$, the red curve\\
%3) When $\frac{F_0}{m\omega_0^2\sigma}=0.5$, the green one.\\
%For those three types of curve, the significant difference is only at low energy case:\\
%For the red one, particle will oscillate at constant frequency $\omega$;
%For the blue one, when energy is lower, since the first derivative of the curve in the neighbourhood is non-zero, the frequency goes to infinity;
%For the green curve, in low energy limit, it takes finite time to finish half period of oscillation, while infinitesimal time is spent on the slope part. Thus, frequency will converge to  $2\omega$.

%\begin{figure}
%\subfigure[]{
%\begin{minipage}[b]{0.3\textwidth}
%\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_1.png} 
%\end{minipage}
%}
%\subfigure[]{
%\begin{minipage}[b]{0.3\textwidth}
%\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_2.png} 
%\end{minipage}
%}
%\subfigure[]{
%\begin{minipage}[b]{0.3\textwidth}
%\includegraphics[scale=0.17]{ZhiyuPictures/freq_scanE_3.png} 
%\end{minipage}
%}
%\centering
%\caption{Frequency of relative motion with internal energy in three regime} Numbers in the legend is the value %of $\frac{F_0}{m\omega_0^2\sigma}$
%\label{fig:thermalization3}
%\end{figure}
%\end{comment}
